A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
improvements of "Benelux"

`r a("Benelux")`:
The Benelux region includes the Netherlands, northern Belgium and large parts of Lower Saxony and North Rhine-Westphalia. All these regions have ^14^C data on graves in Radon-B, but the data density in Belgium and the Netherlands is much higher. As in Southern Scandinavia, the Early Bronze Age is under-represented in the Benelux region as opposed to the Middle and Late Bronze Age, although in a slightly weaker form. While the information density of the *burial type* variable follows this course, *burial construction* is almost undocumented in the Late Bronze Age. As in the *Southern Germany* region, there is a serious difference between the information density of both variables. If one considers the relative development of the variables as they can be derived from the grave data in comparison to the archaeological doctrine, both agreement and deviations result here in detail. Here, too, the study region includes different cultural phenomena with partially diametrically different burial customs, but a general assessment of the conditions is nevertheless possible. In the north and east of the Benelux region body burials were the rule until the Late Bronze Age, while burials on fire dominated earlier in the south of the Meuse. The Radon-B proxy seems to overemphasise the dominance of cremation in the whole area. The relevance of hill burials in the Early and Middle Bronze Age, on the other hand, is correctly reflected, and the mixture between hill and flat graves in the context of urnfields, often resulting from the continued use of existing monumental sites, is also visible.

>>>>

`r a("Benelux")`:
The Benelux region includes the Netherlands, northern Belgium and large parts of Lower Saxony and North Rhine-Westphalia. All these regions have ^14^C data on graves in Radon-B, but the data density in Belgium and the Netherlands is much higher. As in Southern Scandinavia, the Early Bronze Age is under-represented in the Benelux region as opposed to the Middle and Late Bronze Age, although in a slightly weaker form. While the information density of the *burial type* variable follows this course, *burial construction* is almost undocumented in the Late Bronze Age. As in the *Southern Germany* region, there is a serious difference between the information density of both variables. If one considers the relative development of the variables as they can be derived from the grave data in comparison to the archaeological state of research there is both deviation as well as agreement. Here, too, the study region includes different cultural phenomena with highly different burial customs: In the north and east of the Benelux region inhumations were the rule until the Late Bronze Age, while cremation dominated earlier south of the Meuse. The Radon-B proxy seems to overemphasise the dominance of cremation in the whole area. The relevance of hill burials in the Early and Middle Bronze Age, on the other hand, is correctly reflected, and the mixture between hill and flat graves in the context of urnfields, often resulting from the continued use of existing monumental sites, is also visible.
